---
title: "Floating TOC Example"
author: "Your Name"
date: "2025-02-12"
output:
  html_document:
    toc: true
    toc_float: true
---


# Introduction

This is a sample R Markdown document demonstrating how to create a floating table of contents (TOC). With the `toc_float: true` option, the TOC will remain visible as you scroll through the document.

```{r setup, include=FALSE}
# Set global chunk options
knitr::opts_chunk$set(echo = TRUE)
```

# Section 1: Overview

This section provides an overview of the analysis.

## Subsection 1.1: Background

Provide background information here.

## Subsection 1.2: Objectives

Outline the objectives of your analysis.

# Section 2: Data Analysis

This section demonstrates a simple data analysis example.

```{r data-analysis}
# Generate some sample data and plot it
set.seed(123)
data <- rnorm(100)
hist(data, main = "Histogram of Sample Data", xlab = "Data Values")
```

# Section 3: Results

Discuss the results and any findings here.

## Subsection 3.1: Detailed Findings

Go into further details about your findings.

# Section 4: Conclusion

Summarize your conclusions and provide suggestions for future work.
```

To use this sample:

1. Save the content above into a file with an `.Rmd` extension (e.g., `floating_toc_example.Rmd`).
2. Open the file in RStudio or your preferred editor.
3. Knit the document to HTML, and you'll see a floating TOC on the side as you scroll.

Feel free to modify the sections and code chunks to suit your needs!
